\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{indentfirst}
\usepackage{setspace}

\title{PS 1}
\author{Mengyang Davila}

\doublespacing
\begin{document}
\maketitle

\section{Introduction}
\indent Since I took my very first accounting course in 2011, the accounting field has undergone significant transformation. Data science is becoming an important tool for accounting researchers, and it can be applied to a wide range of areas. I am eager to take this course to gain a deeper understanding of data analysis and machine learning techniques. 

I would like to use machine learning algorithm and textual analysis to conduct audit research, which would be otherwise impossible using traditional archival data. As for the project for this class, I want to study the impact of audit committee monitoring role on the quality and timeliness of public firms' voluntary disclosures. To achieve this, I plan to use text mining techniques to identify patterns and trends in audit committee charters that are attached to proxy statements.

After graduation, my goal is to pursue a career in academia by obtaining a tenure-track position at an elite university. Equally important to me is to continue to work hard and be a positive role model for my children.

\section{Equation}

\[a^2 + b^2 = c^2\]

\end{document}